Statistical Searches for Microlensing Events in Large, Non-Uniformly Sampled Time-Domain Surveys: A Test Using Palomar Transient Factory Data

### 2013-10-01 text/final_paper/ms.tex
added durbin-watson thing
removed mention of delta chi squared before defining it

\section{Microlensing event recovery} \label{sec:event_recovery}
Microlensing surveys typically use difference image analysis \citep{alard1998} to identify transient events in raw imaging data. The light curves of transient sources are then analyzed and vetted using a variety of selection methods to search for microlensing event candidates and distinguish them from, e.g., variable stars, outbursting systems, and novae. Surveys have approached this process differently (as described in \citealt{ogle_optical_depth, con_idx, alcock2000, macho_detection_efficiency, udalski03,  hamadache2009, wyrzykowski2009, sumi2011}), but the general idea is to require that: 
\begin{enumerate}
	\item any selected light curve has some number of consecutive data points brighter than some threshold,
	\item compared to flat or linear light-curve models, a microlensing model best describe the data, as determined by using a $\Delta\chi^2$ test, and
	\item the microlensing model event parameters have physically reasonable values.
\end{enumerate}

@@

$\eta$, the von Neumann ratio \citep{von_neumann1941}, is the mean square successive difference divided by the sample variance:
\begin{align}
	\eta = \frac{\delta^2}{\sigma^2} = \frac{\sum^{N-1}_i(x_{i+1} - x_i)^2/(N-1)}{\sigma^2}.
\end{align}
$\eta$ is small when there is strong positive serial correlation between successive data points.

>>>>

\section{Microlensing event recovery} \label{sec:event_recovery}
Microlensing surveys typically use difference image analysis \citep{alard1998} to identify transient events in raw imaging data. The light curves of transient sources are then analyzed and vetted using a variety of selection methods to search for microlensing event candidates and distinguish them from, e.g., variable stars, outbursting systems, and novae. Surveys have approached this process differently (as described in \citealt{ogle_optical_depth, con_idx, alcock2000, macho_detection_efficiency, udalski03,  hamadache2009, wyrzykowski2009, sumi2011}), but the general idea is to require that: 
\begin{enumerate}
	\item any selected light curve has some number of consecutive data points brighter than some threshold,
	\item compared to flat or linear light-curve models, a microlensing model best describe the data, and
	\item the microlensing model event parameters have physically reasonable values.
\end{enumerate}

@@

$\eta$, the von Neumann ratio \citep[][also known as the Durbin-Watson statistic]{von_neumann1941}, is the mean square successive difference divided by the sample variance:
\begin{align}
	\eta = \frac{\delta^2}{\sigma^2} = \frac{\sum^{N-1}_i(x_{i+1} - x_i)^2/(N-1)}{\sigma^2}.
\end{align}
$\eta$ is small when there is strong positive serial correlation between successive data points.
